Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-16 Writing/CEA_3rd_round/replies_rev.rmd
additional figures in appendix

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
---

@@

<span style="color:blue">  
Please see Figure xx in Appendix xx that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly.
</span>

@@

<span style="color:blue">  
We do not say EOIR cannot be estimated by studies mentioned in 28ff. Indeed, any methods can "estimate" EOIR. However, no method can estimate the "true" EONR and we will 
"never" know true EONRs for real fields. We can only esimate them. This principle is at the core of statistical analysis. We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what thye look like. This means that when we try to evaluate how different models perofrm in predicting EONR using real data, we simply do not have a valid benchmark to compare against. Some may ask, then why don't we use models' yield prediction abililty because yield is observable. And this is precisely the dangerous practice that we show is wrong.

Please note that this is a stark contrast to "yield" (not EOIR) prediction because yields ARE observable and models can be verified. However, that is not the case for EOIR. This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher. This way, we can test model's ability to predict EONR, not yield. Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method. This is because we can never test the statistical property of a statistical method in principle using the real data. For example, please see (Shun, cite CF paper here.)

@@

@@

<span style="color:blue">  
Please see page xx, line yy for the precise definition of the RMSE for yield and EONR predictions.
</span>

@@

We actually realized the results presented in Figure 6 is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges. The biggest problem of the relationship we identified is that the maximum profit of the field is very different across simulations (the field in some simulations are simply more profitable than the fields in other simulations). So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average. For this reason, we eliminated the figure and also dropped our cliam that yield prediction and EONR prediction are uncorrelated. Thank you so much for spotting this embarassing mistake from our side.

However, please note that our cliam that better yield prediction does "not necessarily" lead to higher profit remains intact. This is evident in Table 1 and the analysis behind this table is valid. This happens because you can prefict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.

@@

Estiamting the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predicte yield levels at the observed rate for wrong reasons.

@@

Please see Figure xxx that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a sigle simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is.

@@

Please see Figure xxx for illustrations of how yield responds to N site-specifically for xxx sites within a field. Please note that Figure xxx (Figure 5) presents exactly the moldes' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc). As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR. BRF suffers negative bias as well. On the contrary, CF does not suffer this bias. Of couese, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5. On top of negative bias RF and BRF suffer, their estiamtion of the impact of N is also less accurate than CF. That is why CF performs better than RF and BRF in profit. Please note that CF does not even estimate (3). It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield resposne function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We conside those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

>>>>

---
title: "Reply to Editor"
output:
  bookdown::word_document2:
    number_sections: no
    reference_docx: ../word_template_format.docx
bibliography: ../ ML_VRA.bib
---

@@

<span style="color:blue">  
Please see Figure E.1 in Appendix E that shows the convergence of CNN for a single simulation round. We cannot show this kind of figure for all the simulation rounds. But, any interested readers can replicate our work as the codes will be accessible publicly.
</span>

@@

<span style="color:blue">  
We do not say EOIR cannot be estimated by studies mentioned in 28ff. Indeed, any methods can "estimate" EOIR. However, no method can estimate the "true" EONR and we will 
"never" know true EONRs for real fields. We can only estimate them. This principle is at the core of statistical analysis. We never observe how data is generated (the underlying laws that govern how the world works whether it is physical, biological, or economic), but we can "estimate" (approximate) what they look like. This means that when we try to evaluate how different models perform in predicting EONR using real data, we simply do not have a valid benchmark to compare against. Some may ask, then why don't we use models' yield prediction ability because yield is observable. And this is precisely the dangerous practice that we show is wrong.

Please note that this is a stark contrast to "yield" (not EOIR) prediction because yields ARE observable and models can be verified. However, that is not the case for EOIR. This is why you need MC simulations where the data generating process (how yield responds to N, and how field characteristics affect yield response to N) is "known" to the researcher. This way, we can test model's ability to predict EONR, not yield. Any journal article that proposes a new statistical method always accompany the theory of why their method works (consistency of their estimation, etc) with MC simulations where the researchers determines how data is generated and apply their method. This is because we can never test the statistical property of a statistical method in principle using the real data. For example, please see @Wager2018a and @oprescu2019orthogonal

@@

<span style="color:blue">  
The typo was corrected.
</span>

@@

<span style="color:blue">  
Please see page 19, line 323 and 328 for the precise definition of the RMSE for yield and EONR predictions.
</span>

@@

We actually realized the results presented in Figure 6 is completely invalid. As you pointed out the problem with the relationship presented in the figure is basically comparing apples and oranges. The biggest problem of the relationship we identified is that the maximum profit of the field is very different across simulations (the field in some simulations are simply more profitable than the fields in other simulations). So, basically, the observed variation in achieved profits by estimated site-specific EONR is dominated simply by how profitable fields are on average. For this reason, we eliminated the figure and also dropped our claim that yield prediction and EONR prediction are uncorrelated. Thank you so much for spotting this embarrassing mistake from our side.

However, please note that our claim that better yield prediction does "not necessarily" lead to higher profit remains intact. This is evident in Table 1 and the analysis behind this table is valid. This happens because you can predict yield well for a "wrong" reason, attributing parts of variations in yield to something other than its true driver.

@@

Estimating the structure well leads to a better prediction of yield, however better prediction of yield does not necessarily mean a better prediction of the structure of the yield response function (yield response curve) because you can predict yield levels at the observed rate for wrong reasons.

@@

Please see Figure H.1 that plots true yields (without error, epsilon) against predicted yields by model (CF is not presented as it does not predict yield levels as discussed in the article) for a single simulation round. RMSE is presented in the figure as well. As we have 1000 simulations, it is simply infeasible to present figures like this for all the simulation rounds. But, this figure provides a better sense of the value of RMSE and how good the fit is.

@@

Please see Figure F.1 for illustrations of how yield responds to N site-specifically for three sites within a field. Please note that Figure xxx (Figure 5) presents exactly the models' ability to predict the impact of N on yield at different treatments (lowest to the second lowest, second lowest to third lowest, etc). As you can see in the figure, RF underestimates the impact of N on yield severely, which leads to the underestimation of EONR. BRF suffers negative bias as well. On the contrary, CF does not suffer this bias. Of course, the worst of all is CNN, which thinks that the impact of N on yield is almost nascent as you can see in Figure 5. On top of negative bias RF and BRF suffer, their estimation of the impact of N is also less accurate than CF. That is why CF performs better than RF and BRF in profit. Please note that CF does not even estimate (3). It estimates the change in yield when N is increased from one rate to another rate as discussed in the paper.

@@

<span style="color:blue">  
Please see page xx, line xx for a new list of studies that attempt to estimate EONR. Please note that this study has no interest in studies that just predict yield without trying to show how they can use it for EONR estimation. Prediction of yield is almost always not the goal of farmers. We are listing studies that predict yields (or estimate yield response function to be more precise) and then predict EOIR based on them. Also, there is no study that test the performance of EONR using real data. This is because that is fundamentally impossible as we mentioned above. There are studies that predict field-level (not site-specific within a field) EONR for individual fields one by one using a traditional regression approach, then model EONR using ML methods to see how close their estimated field-level EONRs from the trained ML methods are to the EONR "estimated" for individual fields (Shun cite a paper that does this). But, please note that the field-level EONRs they compare against are "estimated." Why did they "estimate" EONR for each field? That is because they do not (and will never) know the true EONR for each field. Moreover, the objective of such studies are fundamentally different from ours. Our focus is on site-specific EONR within a field, theirs' are on field-specific EONR. We conside those studies not very relevant. Including those studies will simply bloat the introduction. 
</span>

### 2022-03-16 Writing/appendix.rmd
additional figures in appendix

>>>>

## Appendix E: CNN performance per training epoch
The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in a single simulation round under aabbyytt scenario.

```{r cnn-epoch, fig.width=5, fig.height=4, fig.cap = "Figure E.1: An example of CNN performance per training epoch (scenario: aabbyytt)"}
knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
```

## Appendix F: MB-yield response curves
The below figure shows some examples of site-specific Mitscherlich-Baule yield function to illustrate how yield responds to N.

```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
vis_MB_curve
```

## Appendix G: The difference between predicting yields and predicting change in yields

```{r, vis-MB-BRF-y, fig.cap = "Figure G.1: Predicted (scenario: aby)"}
vis_MB_BRF_y
```

## Appendix H: True Yields vs Predicted Yields by models

```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure H.1: True yields without error and predicted yields"}
vis_y_pred
```
